\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[a4paper , inner =1.2in , outer =1in , top=1in , bottom=1in, headsep=10pt]{geometry}
\title{\bf \sc WBA Project}
\usepackage[onehalfspacing]{setspace}
\date{\today}
\author{Name: Aminul Haque Dollar}
\begin{document}
	\maketitle
	\section{Introduction to your organization}
		{\bf 1. Introduction to your organization and business unit, outlining the nature of the products/services, markets, demand patterns, company structure and brief history:\\[2ex]Answer: }
		
		My organization is Bangladesh Bank, the central Bank of Bangladesh. Its only head office is situated at the capital city Dhaka and there are ten branches situated outside of Dhaka city. Besides one training academy is also situated at Dhaka. Approximately 6000 (six thousand) employees serve in this bank. Governor is the highest position of the Bank. There are 57(Fifty-seven) departments at the head office which is headed by General Manager (GM) and ten branch offices are also headed by General Manager. 
		Bangladesh Bank is the Central bank and apex regulatory body for the country which was established at December 16, 1971 with effect.
		The major functional areas are:
		
		\begin{itemize}
			\item   Formulation and implementation of monetary and credit policies.
			\item	Regulation and supervision of banks and non-bank financial institutions, promotion and development of domestic financial markets.
			\item	Management of the country's international reserves.
			\item	Issuance of currency notes.
			\item	Regulation and supervision of the payment system.
			\item	Acting as banker to the government.
			\item	Money laundering prevention.
			\item	Collection and furnishing of credit information.
			\item	Implementation of the Foreign exchange regulation Act.
			\item	Managing a deposit insurance scheme.
		\end{itemize}
	
		{\bf 2.	Identify a real and relevant procurement from your organization and business unit to be used as an example and reference point in Section-B. : \\[2ex]Answer:}
		
		
		Our Head Office premises consists of the following major structures:
		\begin{enumerate}
			\item 	One 30 (thirty)-storied building including single basement.
			\item	One 08 (eight) storied building.
			\item	One 07(seven) storied building.
		\end{enumerate}
	
		Mentioned in the above, 08(eight) storied building has been constructed in the year of 1965. This building is occupied by Governor Section and other high official chambers and some important departments.
		
		The toilet blocks of the building are not suitable to use as well as not as hygiene as it supposed to be. Our top management has taken decision to renovate and modernize all the existing toilet blocks of the building. Depending on that decision, we have started to mend the executive floor toilet blocks first.\\[2ex]
		
		\textbf{Detailed description of the project:}
		\begin{enumerate}
			\item 	Name of the Project: Renovation and Modernization of Existing Toilet Block at Executive Floor of Bangladesh Bank 08(eight) storied Main Building, Head Office, Dhaka.
			\item	Total Contraction Area: $1600 ft^2 \;(approx).$ 
			\item 	Estimated project costs: $BDT\; 1,80,00,000/00$ ($BDT$ One Crore eighty lac) only.
			\item 	Project Completion time: 06 (six) months after the issuance of Award of Contract.
			\item 	Procurement Method: Open bid competition through Invitation to Bid (ITB).
			\item Work consists of:
			\begin{itemize}
				\item[\bf Part A:]
				{\bf  Civil works-}\\Dismantling work, Brick wall, Tiles/Granite works, concrete reinforcement work, Steel reinforcement work, Cement plastering, wooden door frame \& shutter, painting works, Aluminum frame with glass window, Metal perforated false ceiling etc. works.
				\item[\bf Part B:]
				{\bf Sanitary \& Plumbing works-}\\Water supply pipe fitting, Foreign made Commode, Wash hand basin, Urinal, Toilet paper holder, Automatic hand drawer, Sensor type soap dispenser, Bib cock, Stop cock, Pillar Cock, Hand shower, Water purifier, geyser etc.
				\item[\bf Part C:]
				\textbf{Electrical works-}\\Electric cable wiring, installation of foreign made switch, socket, circuit bracer, $SDB$, $MDB$, Environment friendly LED light, Exhaust fan etc. works.
				\item[\bf Part C:]
				\textbf{Mechanical Works-}\\Air Conditioning system
				
				
				
			\end{itemize}
			
		\end{enumerate}
		
	
	
\end{document}

